% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Expérience Professionelle}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {June 2017}   {Android Developer}{Airtel Payments Bank}{Gurgaon}
    {Till Date} {
                      \begin{itemize}
                        \item Responsible for Payments bank on MyAirtel android app.                         
                        \item Responsible for coding, testing, debugging, code review and deployment.
                         \item Responsible for Architectural Improvement - Flexibility and adaptability to different frameworks and architectures. 
                      \end{itemize}
                    }
                    {Android, JAVA, Kotlin, Spring boot, Firebase, Fabric, SQL, GIT, JIRA, Appium, Kibana, AeroSpike }
  \emptySeparator
  \experience
    {Aug 2015}   {Sr. Software Engineer}{Affle AppStudios Pvt. Ltd.}{Gurgaon}
    {May 2017} {
                      \begin{itemize}
                        \item Responsible for coding, testing, debugging and deployment.
                        \item Responsible for code optimization and User Experience improvement for different sets of users.
                        \item Ensuring delivery of projects in time.
                        \item Dealing with clients in order to understand the requirements so that we can deliver 100 percent. 
                      \end{itemize}
                    }
                    {Android, JAVA, Design patterns, Attribution SDKs, Payments SDKs, Firebase, GIT }
  \emptySeparator
  \experience
    {July 2014}   {Mobile Application Developer}{Bitmetric Technologies Pvt Ltd. }{Noida}
    {July 2015} {
                      \begin{itemize}
                        \item Responsible for design, development, testing, debugging and deployment of Android Applications and Hybrid Mobile Applications. 
                        \item Research and experiment on different technologies to get the best for the apps. 
                        \item Worked on monetisation of the exiting applications as well as new applications.
                      \end{itemize}
                    }
                    {Android, JAVA, JavaScript, JQuery, HTML, SPA, Cordova, Web Scraping, Admob }
  \emptySeparator
\end{experiences}
