% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\pagebreak
\sectionTitle{Project - Highlights}{\faLaptop}

\begin{projects}
    \project
	{\website{https://play.google.com/store/apps/details?id=com.myairtelapp}{Airtel Payments Bank - MyAirtel}}{June 2017 - Till Date}
	{ \textit{Downloads: 50M+, Play Store Rating: 4.4}}
{ Airtel Payments Bank is India’s first payments bank, with operations across all 29 States of India. It is a fully digital and paperless bank and aims to take basic banking services to the doorstep of every Indian and contribute to the Government’s vision of Financial Inclusion and Digital India.}
	{Android, JAVA, Kotlin, Gradle, Firebase, MVP, Design Patterns, Volley, Firebase, Caching, Fabric, SpringBoot}
    	\linebreak
        
          \project
	{\website{http://www.careergod.com/}{CareerGOD}}{Aug 2016-  Feb 2017}
	{\textit{CareerGOD is app for FIITJEE LTD.}}
{CareerGOD helps students to find the most suitable college for themselves as per their academic profile in India and US. Application includes fallowing features such as  Details of college, Student' chance to get into a certain college, Spend Calculator with graphical representation, Return on Investment, Upcoming Events (Custom Calendar), College subscription to get updates etc. }
	{Android, JAVA, DeepLinks, AppIndexing, Custom calendar, FCM, SyncAdapter, Material design, Offline Data caching}    
    \linebreak
    
    	\project
	{\website{https://play.google.com/store/apps/details?id=com.app.extramarks.emilly}{English Speaking App – EMILLY}}{Oct 2015-  May 2016}
	{\textit{Downloads: 100,000+, Play Store Rating: 4.2}}
{EMILLY (Extramarks Interactive Language Learning for You) is a Spoken English app especially developed and designed for Hindi speaking users who aspire to become confident English speakers. 
EMILLY’s interactive learning modules are carefully planned to improve listening, speaking, reading and writing skills. }
	{JAVA, Android, Multi-Language Support, Custom UI Components, Material Design, Animations, Media Content, Speech to text, In-App Purchase}
    \linebreak
    
	 	\project
	{\website{https://play.google.com/store/apps/details?id=bitmetric.android.colregs}{IMO Collision Regulations}}{Aug 2014-  Oct 2014}
	{\textit{Downloads: 100,000+, Play Store Rating: 4.5}}
{The International Regulations for Preventing Collisions at Sea 1972, also known as "COLREGs", "Rules of the Road" or "RoR", prescribe rules to be followed by ships and other vessels at sea in order to prevent collisions between two or more vessels.}
	{ Android, JAVA, JavaScript, JQuery, Html, SPA}
	 \linebreak
     
       	\project
	{\website{https://play.google.com/store/apps/details?id=bitmetric.android.colregs}{tinysurprise - Online Gifting}}{Aug 2013-  Jan 2014}
		{\textit{Downloads: 10,000+, Play Store Rating: 4.5}}
{tinySurprise is a Online gifting MegaStore that intends to deliver the beautiful moments!}
	{Android, JAVA, SQLite, Payment SDKs, Facebook SDK, Google SDK, PHP}
	 \linebreak
\end{projects}